Multiple Dice Working as One: CAD Flows and Routing Architectures for Silicon Interposer FPGAs

### 2014-12-14 doc/journal/fpgapaperfinal/FPGAPaper/partitioning.tex
Added metis and hmetis references
git-svn-id: https://vtr-verilog-to-routing.googlecode.com/svn/branches/javeed@4527 8e3573b8-cf2c-4f14-ef6d-137439e28b8b
Updated my figures to look more like Ehsan's.
git-svn-id: https://vtr-verilog-to-routing.googlecode.com/svn/branches/javeed@4537 8e3573b8-cf2c-4f14-ef6d-137439e28b8b

\subsubsection{Partitioning Tool}
Two well-known freely available graph partitioning tools are Metis [] and hMetis []. Metis operates on graphs, while hMetis operates on hypergraphs -- a hypergraph is a generalization of a graph, where each edge can connect any number of vertices. It is most natural to represent a circuit netlist as a hypergraph, where the vertices are netlist pins (or blocks) and the hyperedges are the nets joining the pins. Based on that criterion alone, hMetis is the most appropriate choice of partitioner. However, there are other issues to consider for the circuit netlist partitioning use case.

@@

\begin{figure}[!htbp]
\centering
\includegraphics[width=\linewidth]{graph_topology_cutsize.eps}
\caption{Hypergraph cut size achieved by Metis with different hyperedge models and weightings. n is the number of vertices on a hyperedge.}
\label{fig:graph_topology_cutsize}
\end{figure}

@@

\begin{figure}[!htbp]
\centering
\includegraphics[width=\linewidth]{graph_topology_mcw.eps}
\caption{Minimum channel width achieved by VPR with different hyperedge models and weightings. n is the number of vertices on a hyperedge.}
\label{fig:graph_topology_mcw}
\end{figure}

@@

\begin{figure}[!htbp]
\centering
\includegraphics[width=\linewidth]{vpr_flows_mcw.eps}
\caption{Minimum channel width achieved by VPR with the different partitioning flows.}
\label{fig:flows_mcw}
\end{figure}

@@

\begin{figure}[!htbp]
\centering
\includegraphics[width=\linewidth]{vpr_flows_crit_path.eps}
\caption{Critical path delay achieved by VPR with the different partitioning flows.}
\label{fig:flows_crit_path}
\end{figure}

@@

\begin{figure}[!htbp]
\centering
\includegraphics[width=\linewidth]{wires_cut.eps}
\caption{Impact of partitioning-based CAD flow on routability for a range of architectures.}
\label{fig:wires_cut}
\end{figure}

@@

\begin{figure}[!htbp]
\centering
\includegraphics[width=\linewidth]{packing_bloat.eps}
\caption{Packing bloat.}
\label{fig:packing_bloat}
\end{figure}

>>>>

\subsubsection{Partitioning Tool}
Two well-known freely available graph partitioning tools are Metis~\cite{karypis1998multilevelmetis} and hMetis~\cite{karypis1999multilevelhmetis}. Metis operates on graphs, while hMetis operates on hypergraphs -- a hypergraph is a generalization of a graph, where each edge can connect any number of vertices. It is most natural to represent a circuit netlist as a hypergraph, where the vertices are netlist pins (or blocks) and the hyperedges are the nets joining the pins. Based on that criterion alone, hMetis is the most appropriate choice of partitioner. However, there are other issues to consider for the circuit netlist partitioning use case.

@@

\begin{figure}[!htbp]
\centering
%\includegraphics[width=\linewidth]{graph_topology_cutsize.eps}
%\input{graph_topology_cutsize.tex}
\input{graph_topology_cutsize}
\caption{Hypergraph cut size achieved by Metis with different hyperedge models and weightings. n is the number of vertices on a hyperedge.}
\label{fig:graph_topology_cutsize}
\end{figure}

@@

\begin{figure}[!htbp]
\centering
\input{graph_topology_mcw}
%\includegraphics[width=\linewidth]{graph_topology_mcw.eps}
\caption{Minimum channel width achieved by VPR with different hyperedge models and weightings. n is the number of vertices on a hyperedge.}
\label{fig:graph_topology_mcw}
\end{figure}

@@

\begin{figure}[!htbp]
\centering
%\includegraphics[width=\linewidth]{vpr_flows_mcw.eps}
\input{vpr_flows_mcw}
\caption{Minimum channel width achieved by VPR with the different partitioning flows.}
\label{fig:flows_mcw}
\end{figure}

@@

\begin{figure}[!htbp]
\centering
\input{vpr_flows_crit_path}
\caption{Critical path delay achieved by VPR with the different partitioning flows.}
\label{fig:flows_crit_path}
\end{figure}

@@

\begin{figure}[!htbp]
\centering
\input{wires_cut}
\caption{Impact of partitioning-based CAD flow on routability for a range of architectures.}
\label{fig:wires_cut}
\end{figure}

@@

\begin{figure}[!htbp]
\centering
\input{packing_bloat}
\caption{The number of blocks in the clustered netlist with and without partitioning constraints. This is a measure of packing bloat.}
\label{fig:packing_bloat}
\end{figure}
